Paper notes

### 2019-08-06 paper_notes.Rmd
updated 05_08
ok parameter for abm

```{r testing logistic}

# prob <- function(e_w,s,t,v_w,p,q){1 / (1 + exp(-e_w*(d_u_e)) + exp(-v_w*(d_u_v)))}

# Make: foreach d_u_e [0-1], v_u_e spans within each [0-1]

prob1 <- prob(100,300,100,1,100,100)

plot(prob1)
```

>>>>

```{r logistic putting as in abm ethnic_weight, value_weight}

prob <- function(d_u_e,d_u_v,e_w,par_v){round(1 / (1 + exp(-(e_w*10)*(d_u_e) + (-(v_w*10)*(d_u_v)))),digits= 2)}

for (d_u_e in seq (-1.0,1.0, by = 0.1)){

e_w <- 0
v_w <- 0

# d_u_e <- -1

  dis_0   <- prob(d_u_e,0.0,e_w,v_w)
dis_0.1 <- prob(d_u_e,0.1,e_w,v_w)
dis_0.2 <- prob(d_u_e,0.2,e_w,v_w)
dis_0.3 <- prob(d_u_e,0.3,e_w,v_w)
dis_0.4 <- prob(d_u_e,0.4,e_w,v_w)
dis_0.5 <- prob(d_u_e,0.5,e_w,v_w)
dis_0.6 <- prob(d_u_e,0.6,e_w,v_w)
dis_0.7 <- prob(d_u_e,0.7,e_w,v_w)
dis_0.8 <- prob(d_u_e,0.8,e_w,v_w)
dis_0.9 <- prob(d_u_e,0.9,e_w,v_w)
dis_1   <- prob(d_u_e,1.0,e_w,v_w)
dis_0.1neg <- prob(d_u_e,-0.1,e_w,v_w)
dis_0.2neg <- prob(d_u_e,-0.2,e_w,v_w)
dis_0.3neg <- prob(d_u_e,-0.3,e_w,v_w)
dis_0.4neg <- prob(d_u_e,-0.4,e_w,v_w)
dis_0.5neg <- prob(d_u_e,-0.5,e_w,v_w)
dis_0.6neg <- prob(d_u_e,-0.6,e_w,v_w)
dis_0.7neg <- prob(d_u_e,-0.7,e_w,v_w)
dis_0.8neg <- prob(d_u_e,-0.8,e_w,v_w)
dis_0.9neg <- prob(d_u_e,-0.9,e_w,v_w)
dis_1neg   <- prob(d_u_e,-1.0,e_w,v_w)

  value_difference <- seq(-1.0,1.0, by = 0.1)
  prob_relocation <- seq(0.0, 1.0,  by = 0.1)

  prob_choice <- c(dis_1neg,dis_0.9neg,dis_0.8neg,dis_0.7neg,dis_0.6neg,dis_0.5neg,dis_0.4neg,dis_0.3neg,dis_0.2neg,dis_0.1neg,dis_0,dis_0.1,dis_0.2,dis_0.3,dis_0.4,dis_0.5,dis_0.6,dis_0.7,dis_0.8,dis_0.9,dis_1)

  name_diff <- paste0("Note: "," Ethnic parameter = ", e_w*10," ;"," Value parameter = ", v_w*10, 
                      "\r\n Utility Difference -1 = MIN Utility Alternative, 1 = MAX Utility Alternative")

  name_diff_title <-paste0("Probability to move to alternative","\r\n Difference Ethnic Utility (Alternative - Current) = ", d_u_e)

plot(value_difference,prob_choice, xlab = "x-axis: Difference Value Utility (Alternative - Current) \r\n",ylab = "probability", main = name_diff_title, sub = name_diff,ylim = c(0,1), yaxt = 'n')
axis(2,at=seq(0.0, 1.0, by = 0.25))

```{r logistic in sequence, to test with parameters, to be deleted}

prob <- function(d_u_e,d_u_v,par_e,par_v){round(1 / (1 + exp(-par_e*(d_u_e) + (-par_v*(d_u_v)))),digits= 2)}

for (d_u_e in seq (-1.0,1.0, by = 0.1)){

par_e <- 10
par_v <- 10 - par_e

# d_u_e <- -1

  dis_0p   <- prob(d_u_e,0.0,par_e,par_v)
dis_0.1p <- prob(d_u_e,0.1,par_e,par_v)
dis_0.2p <- prob(d_u_e,0.2,par_e,par_v)
dis_0.3p <- prob(d_u_e,0.3,par_e,par_v)
dis_0.4p <- prob(d_u_e,0.4,par_e,par_v)
dis_0.5p <- prob(d_u_e,0.5,par_e,par_v)
dis_0.6p <- prob(d_u_e,0.6,par_e,par_v)
dis_0.7p <- prob(d_u_e,0.7,par_e,par_v)
dis_0.8p <- prob(d_u_e,0.8,par_e,par_v)
dis_0.9p <- prob(d_u_e,0.9,par_e,par_v)
dis_1p  <- prob(d_u_e,1.0,par_e,par_v)
dis_0.1negp <- prob(d_u_e,-0.1,par_e,par_v)
dis_0.2negp <- prob(d_u_e,-0.2,par_e,par_v)
dis_0.3negp <- prob(d_u_e,-0.3,par_e,par_v)
dis_0.4negp <- prob(d_u_e,-0.4,par_e,par_v)
dis_0.5negp <- prob(d_u_e,-0.5,par_e,par_v)
dis_0.6negp <- prob(d_u_e,-0.6,par_e,par_v)
dis_0.7negp <- prob(d_u_e,-0.7,par_e,par_v)
dis_0.8negp <- prob(d_u_e,-0.8,par_e,par_v)
dis_0.9negp <- prob(d_u_e,-0.9,par_e,par_v)
dis_1negp   <- prob(d_u_e,-1.0,par_e,par_v)

  value_difference <- seq(-1.0,1.0, by = 0.1)
  prob_relocation <- seq(0.0, 1.0,  by = 0.1)

  prob_choicep <- c(dis_1negp,dis_0.9negp,dis_0.8negp,dis_0.7negp,dis_0.6negp,dis_0.5negp,dis_0.4negp,dis_0.3negp,dis_0.2negp,dis_0.1negp,dis_0p,dis_0.1p,dis_0.2p,dis_0.3p,dis_0.4p,dis_0.5p,dis_0.6p,dis_0.7p,dis_0.8p,dis_0.9p,dis_1p)

  name_diff <- paste0("Note: "," Ethnic parameter = ", par_e," ;"," Value parameter = ", par_v, 
                      "\r\n Utility Difference -1 = MIN Utility Alternative, 1 = MAX Utility Alternative")

  name_diff_title <-paste0("Probability to move to alternative","\r\n Difference Ethnic Utility (Alternative - Current) = ", d_u_e)

plot(value_difference,prob_choicep, xlab = "x-axis: Difference Value Utility (Alternative - Current) \r\n",ylab = "probability", main = name_diff_title, sub = name_diff,ylim = c(0,1), yaxt = 'n')
axis(2,at=seq(0.0, 1.0, by = 0.25))
